\documentclass[journal,12pt,onecolumn]{IEEEtran}

% Import necessary packages
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
\usepackage{gvv}                                        
\usepackage[latin1]{inputenc}                                
\usepackage{color} 
\usepackage{enumitem} % Include this package
\usepackage{array}                                            
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\usepackage{tabularx}
\usepackage{array}
\usepackage{float}
\usepackage{multicol} % Add the multicol package
\usepackage{circuitikz}
\usepackage{textcomp}
% New theorem declarations
\newtheorem{theorem}{Theorem}[section]
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{example}{Example}[section]
\newtheorem{definition}[problem]{Definition}

% Custom command definitions
\newcommand{\BEQA}{\begin{eqnarray}}
\newcommand{\EEQA}{\end{eqnarray}}
\newcommand{\define}{\stackrel{\triangle}{=}}

\theoremstyle{remark}
\newtheorem{rem}{Remark}

% Document begins here
\begin{document}
\bibliographystyle{IEEEtran}
\vspace{3cm}

% Title of the document
\title{ASSIGNMENT 7}
\author{EE24BTECH11011 - PRANAY}
\maketitle

\bigskip

% Custom figure and table numbering
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\subsection{\textbf{Q.1 to Q.5 carry one mark each}}
   \begin{enumerate}
  \item  "The dress \rule{3cm}{0.15mm} her so well that they all immediately \rule{3cm}{0.15mm} her on her
appearance."
The words that best fill the blanks in the above sentence are
\begin{enumerate}
    \item complemented, complemented
    \item complimented, complemented
    \item  complimented, complimented
    \item complemented, complimented
\end{enumerate}
\item "The judge's standing in the legal community, though shaken by false allegations of
wrongdoing, remained \rule{3cm}{0.15mm}."\\
The word that best fills the blank in the above sentence is
\begin{multicols}{4}
\begin{enumerate}
    \item  undiminished \item  damaged \item  illegal \item  uncertain
\end{enumerate}
\end{multicols}
\item Find the missing group of letters in the following series :\\
BC, FGH, LMNO, \rule{3cm}{0.15mm}
\begin{multicols}{4}
    \begin{enumerate}
        \item  UVWXY \item  TUVWX \item  STUVW \item  RSTUV
    \end{enumerate}
\end{multicols}
\item The perimeters of a circle, a square and an equilateral triangle are equal. Which one of the
following statements is true?
\begin{enumerate}
    \item The circle has the largest area.
\item  The square has the largest area.
\item  The equilateral triangle has the largest area.
\item  All the three shapes have the same area.
\end{enumerate}
\item The value of the expression $\frac{1}{1+\log_u{vw}}+\frac{1}{1+\log_v{uw}}+\frac{1}{1+\log_w{uv}}$ is \rule{3cm}{0.15mm}
\begin{multicols}{4}
    \begin{enumerate}
        \item $-1$
        \item $0$
        \item $1$
        \item $3$
    \end{enumerate}
\end{multicols}
\subsection{\textbf{Q. 6 - Q. 10 carry two marks each.}}
\item Forty students watched films $A$, $B$ and $C$ over a week. Each student watched either only
one film or all three. Thirteen students watched film $A$, sixteen students watched film $B$
and nineteen students watched film $C$. How many students watched all three films?
\begin{multicols}{4}
    \begin{enumerate}
        \item $0$ \item $2$ \item $4$ \item $8$
    \end{enumerate}
\end{multicols}
\item A wire would enclose an area of $1936 m^2$, if it is bent into a square. The wire is cut into
two pieces. The longer piece is thrice as long as the shorter piece. The long and the short
pieces are bent into a square and a circle, respectively. Which of the following choices is
closest to the sum of the areas enclosed by the two pieces in square meters?
\begin{multicols}{4}
    \begin{enumerate}
        \item  $1096$ \item  $1111$ \item  $1243$ \item  $2486$
    \end{enumerate}
\end{multicols}
\item A contract is to be completed in $52$ days and $125$ identical robots were employed, each
operational for $7$ hours a day. After $39$ days, five-seventh of the work was completed. How
many additional robots would be required to complete the work on time, if each robot is
now operational for $8$ hours a day?
\begin{multicols}{4}
    \begin{enumerate}
        \item $50$
        \item $89$
        \item $146$
        \item $175$
    \end{enumerate}
\end{multicols}
\item A house has a number which needs to be identified. The following three statements are
given that can help in identifying the house number.
\begin{enumerate}[label=\roman*.]
\item If the house number is a multiple of 3, then it is a number from 50 to 59.
\item  If the house number is NOT a multiple of 4, then it is a number from 60 to 69.
\item  If the house number is NOT a multiple of 6, then it is a number from 70 to 79.
\end{enumerate}
What is the house number?
\begin{multicols}{4}
    \begin{enumerate}
        \item $54$ \item $65$ \item $66$ \item $76$
    \end{enumerate}
\end{multicols}
\item An unbiased coin is tossed six times in a row and four different such trials are conducted.
One trial implies six tosses of the coin. If H stands for head and T stands for tail, the
following are the observations from the four trials:
$\brak{1}$ HTHTHT $\brak{2}$TTHHHT $\brak{3}$ HTTHHT $\brak{4}$ HHHT\rule{0.5cm}{0.14mm} \rule{0.5cm}{0.14mm}\\
Which statement describing the last two coin tosses of the fourth trial has the highest
probability of being correct?
\begin{enumerate}
\item  Two T will occur.
\item  One H and one T will occur.
\item  Two H will occur.
\item  One H will be followed by one T.
\end{enumerate}
\end{enumerate}
\subsection{\textbf{Q. 1 - Q. 25 carry one mark each}}
\begin{enumerate}
    \item Let $\vec{a} , \vec{b}$ be two distinct vectors that are not parallel. The vector $\vec{c} = \vec{a} \times \vec{b}$ is 
    \begin{enumerate}
        \item zero
        \item orthogonal to $\vec{a}$ alone.
        \item orthogonal to $\vec{a}+\vec{b}$
        \item orthogonal to $\vec{b}$ alone.
    \end{enumerate}
    \item Consider the function $f\brak{x,y} = \frac{x^2}{2}+\frac{y^2}{3} -5$. All the roots of this function
    \begin{enumerate}
\item  form a finite set of points.
\item  lie on an elliptical curve.
\item  lie on the surface of a sphere.
\item  lie on a hyperbolic curve
\end{enumerate}
\item Consider a vector field given by $x\hat{i}+y\hat{j}+z\hat{k}$ . This vector field is
\begin{enumerate}
\item  divergence-free and curl-free.
\item  curl-free but not divergence-free.
\item  divergence-free but not curl-free.
\item  neither divergence-free nor curl-free.
\end{enumerate}
\end{enumerate}

      
       \end{document}
